An New Search for Supernova Remnants in NGC\,6946

### 2019-01-07 ms.tex
Updates to figures

\todo[inline]{WPB: This will likely have to get shortened further before submission.}

@@

\todo[inline]{WPB: For the Overview Figure, I like the version that shows the galaxy light (currently Fig. 2).  Then in addition to the overview figure, we should show an enlargement of a smaller region in a multi-panel format, showing the subtracted data.  Perhaps this could be done in conjunction with the following paragraph:  Show a small region with several \hii\ regions and SNRs, where the color panel shows the SNRs standing out in different color.  Could include ratio panels as well.}

@@

\todo[inline]{Add symbols to Fig. 1 overview and reference the Figure again here?  I note below we intend to also indicate those observed spectroscopically with a separate symbol or different color.  Could be tricky. WPB}

@@

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.  Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions for comparison purposes in both 2014 and 2015.
Figure \ref{fig_overview} shows all the objects from the sample for which we obtained spectra (red boxes).

@@

The data were processed using standard procedures  from the {\tt gemini} package in IRAF  for bias subtraction, flat-fielding, wavelength calibration, and combination of spectra with different grating tilts to provide the final results.  
Flux calibration was based on baseline GMOS observations of a few spectrophotometric standard stars, carried out in the same semester as part of standard GMOS operations.  
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final background-subtracted object spectra.
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the selection of a representative local background was done on a best-effort basis.  
We then performed  fits to obtain emission line fluxes  from the spectra, assuming Gaussian profiles.  We performed fits for various lines and line complexes:  \hb\ alone,  the \oiii\ doublet,  the \oi\ doublet,  the \ha-\nii\ region, and   the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of all lines in each complex was the same.

@@

We identified 147 candidate SNRs from the WIYN interference images; of these we obtained spectra of 102. The spectra were needed to improve our confidence that the \sii:\ha\ ratios of the emission nebulae were indeed high and to begin to characterize the SNRs using accurate line ratios.  The spectroscopic ratios are shown as a function of GCD in the left panel of  Fig.\ \ref{fig_s2_ha}. \hii\ regions and \oiii-selected objects are shown in blue while nominal \sii:\ha\ candidates from imaging are shown in red.   Conventionally, emission nebulae are identified as SNRs optically, if the \sii:\ha\ ratio exceeds 0.4; 89 of the 102 SNRs with spectra satisfy this criterion, and so we regard these as confirmed SNRs (and they have been listed as such in Table \ref{table_candidates}. Clearly, given uncertainties in derived line ratios for faint emission line objects, a dividing line of 0.4 is somewhat arbitrary, and objects just above (or just below) this ratio should be judged with more context.  For example, slightly under-subtracting contaminating \ha\ emission could readily explain why some candidates ended up below the threshold in the spectroscopic analysis. Likewise, a slight over-subtraction of \ha\ could enhance the \sii:\ha\ ratio derived, potentially pushing some objects above the threshold.  The observed tendency to see higher \sii:\ha\ ratios closer to the nucleus is likely to be at least partly an abundance effect; similar trends are seen in M33 \citep{long18} and in M83 \citep{winkler17}.

@@

Some of the line ratios show indications of a metallicity gradient as evidenced in Fig. \ref{fig_metal_ratios}.  However, unlike the case in M33, what is seen in both the \nii:\ha\ and \sii:\ha\ ratio is that the upper envelope of both plots decreases with radius, but there are examples of SNRs with low ratios at all galactocentric distances.

@@

\appendix

\section{Possible additions to and notes concerning the paper
}
\todo[inline]{Frank put some questions about things one could to in the paper.  ksl has begun to delete them as they are worked off, or given as other inline comments, or if things are out of scope (e.g plots with SNR diameters for this paper.}
Here are some figures we may wish to show, and points we may want to discuss (note: KSL has done some of these figures on Evernote; those all show \oiii-selected objects, which we may choose to omit):
\begin{enumerate}
    \item Correlation between flux from spectra vs imaging (M83 paper, fig 5)  ksl - I have looked at this.  The correlation is there but quite rough.  I'm not sure it is helpful for the paper

\end{enumerate}

@@

\begin{figure}
\plottwo{fig_s2_ha_ratio_distance.pdf}{fig_spec_im_comp.pdf}
\caption{Left: The \sii:\ha\ ratio obtained spectroscopically for SNR candidates (red) and \hii\ regions (blue) as a function of galactocentric distance, R.  Objects with ratios greater than 0.4 (the dashed line) are spectroscopically confirmed SNRs.  Objects near the dividing line are less certain because observational errors in the ratio and/or \hii\ contamination can impact the derived ratio. Right: The \sii:\ha\ ratio derived from spectra compared to that derived from narrow band imaging.  The tendency for spectroscopic ratios to be somewhat higher is consistent with mild impacts from \nii\ emission getting through the \ha\ imaging filter. (This figure needs a 1:1 line to guide the eye, and remove the dashed line at 0.4 for this one--Bill) \label{fig_s2_ha}}

@@

\begin{figure}
\plotone{fig_s2_ratio.pdf}
\caption{The [S II]6717:[S II]6731 line ratio for SNR candidates as a function of galactocentric distance.  THis ratio is nominally a density diagnostic, and most candidates are near the low density limit of 1.4, indicating generally low ISM densities. Derived values above 1.4 are non-physical, and are indicative of errors in the derived ratio.  Only a handful of objects appear to show densities significantly above the low-density limit.  There is no obvious trend with galactocentric distance.  \label{fig_s2_ratio}}
\end{figure}

@@

\begin{figure}
\plottwo{fig_n2_ha_gc.pdf}{fig_s2_ha_gc.pdf}
\caption{Line ratios as a function of GCD.  (I assume the right panel is actually \sii:\ha?  Also, maybe show the H II regions on these plots as well?  Bill) \label{fig_metal_ratios}}

@@

>>>>

% \todo[inline]{WPB: This will likely have to get shortened further before submission.}

@@

\todo[inline]{For the Overview Figure, ksl and wpb like the version that shows the galaxy light (currently Fig. 2).  Frank is responsible for updating the overview figures, and describing them in the text.  Bill is responsible for one or more snap shot  region figures to show what objects we select. Then in addition to the overview figure, we should show an enlargement of a smaller region in a multi-panel format, showing the subtracted data.  He is also responsible for the associated text. .}

@@

\todo[inline]{ksl - It might be worthwhile to have a few sentences of comparison here to our work on M83 where the Magellen seeing made if far easier to see extended emission, and in M33 of course where all of the SNRs are resolved.  This is about the limit of what we can do from the ground, particularly with the seeing we had with WYIN.  To do better, one needs better seeing.}

@@

\todo[inline]{We need a consistent story about the HII regions.  We mention that we selected some O3 objects.  We got spectra of 24 of these.   We have another 41 spectra of HII regions along the slit.  We got very few HII regions just by chance, though these are included in the 41.  It's hard to actually parse out the history of which are which.}

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.  Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions for comparison purposes in both 2014 and 2015.
Figure \ref{fig_overview} shows all the SNR candidates from the sample for which we obtained spectra (red boxes).

@@

The data were processed using standard procedures  from the {\tt gemini} package in IRAF  for bias subtraction, flat-fielding, wavelength calibration, and combination of spectra with different grating tilts to provide the final results.  
Flux calibration was based on baseline GMOS observations of a few spectrophotometric standard stars, carried out in the same semester as part of standard GMOS operations.  
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final background-subtracted object spectra.  
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the selection of a representative local background was done on a best-effort basis.    In addition to the targeted SNR candidates and HII regions, we extracted spectra from other HII regions which appeared by chance in the slits when this was possible.   This allowed us to increase our sample of HII regions from 24 to 65.
We then performed  fits to obtain emission line fluxes  from the spectra, assuming Gaussian profiles.  We performed fits for various lines and line complexes:  \hb\ alone,  the \oiii\ doublet,  the \oi\ doublet,  the \ha-\nii\ region, and   the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of all lines in each complex was the same.

@@

We identified 147 candidate SNRs from the WIYN interference images; of these we obtained spectra of 102. The spectra were needed to improve our confidence that the \sii:\ha\ ratios of the emission nebulae were indeed high and to begin to characterize the SNRs using accurate line ratios.  The spectroscopic ratios are shown as a function of \ha\ flux in the left panel of  Fig.\ \ref{fig_s2_ha}. \hii\ regions and \oiii-selected objects are shown in blue while nominal \sii:\ha\ candidates from imaging are shown in red.   Conventionally, emission nebulae are identified as SNRs optically, if the \sii:\ha\ ratio exceeds 0.4; 89 of the 102 SNRs with spectra satisfy this criterion, and so we regard these as confirmed SNRs (and they have been listed as such in Table \ref{table_candidates}. Clearly, given uncertainties in derived line ratios for faint emission line objects, a dividing line of 0.4 is somewhat arbitrary, and objects just above (or just below) this ratio should be judged with more context.  For example, slightly under-subtracting contaminating \ha\ emission could readily explain why some candidates ended up below the threshold in the spectroscopic analysis. Likewise, a slight over-subtraction of \ha\ could enhance the \sii:\ha\ ratio derived, potentially pushing some objects above the threshold.  The observed tendency to see higher \sii:\ha\ ratios closer to the nucleus is likely to be at least partly an abundance effect; similar trends are seen in M33 \citep{long18} and in M83 \citep{winkler17}.

@@

Some of the line ratios show indications of a metallicity gradient as evidenced in Fig. \ref{fig_metal_ratios}.  However, unlike the case in M33, what is seen in both the \nii:\ha\ and \sii:\ha\ ratio is that the upper envelope of both plots decreases with radius, but there are examples of SNRs with low ratios at all galactocentric distances.   There is a good correlation between the \nii:\ha\ and \sii:\ha\ ratios of the various object as shown in Fig. \ref{fig_s2_n2}.

@@

@@

\begin{figure}
\plottwo{fig_s2_ha_ratio.pdf}{fig_spec_im_comp.pdf}
\caption{Left: The \sii:\ha\ ratio obtained spectroscopically for SNR candidates (red) and \hii\ regions (blue) as a function of \ha flux in the spectrum.  Objects with ratios greater than 0.4 (the dashed line) are spectroscopically confirmed SNRs.  Objects near the dividing line are less certain because observational errors in the ratio and/or \hii\ contamination can impact the derived ratio. Right: The \sii:\ha\ ratio derived from spectra compared to that derived from narrow band imaging.  The tendency for spectroscopic ratios to be somewhat higher is consistent with mild impacts from \nii\ emission getting through the \ha\ imaging filter.  \label{fig_s2_ha}}

@@

\begin{figure}
\plotone{fig_s2_ratio.pdf}
\caption{The [S II]6717:[S II]6731 line ratio for SNR candidates as a function of galactocentric distance.  This ratio is nominally a density diagnostic, and most candidates are near the low density limit of 1.4, indicating generally low ISM densities. Derived values above 1.4 are non-physical, and are indicative of errors in the derived ratio.  Only a handful of objects appear to show densities significantly above the low-density limit.  There is no obvious trend with galactocentric distance.  \label{fig_s2_ratio}}
\end{figure}

@@

\begin{figure}
\plottwo{fig_n2_ha_gc.pdf}{fig_s2_ha_gc.pdf}
\caption{Line ratios of [N II]:\ha\ and [S II]:\ha\ as a function of GCD.  Both SNR candidates and HII regions are shown.     \label{fig_metal_ratios}}

@@

\begin{figure}
\plotone{fig_s2_n2.pdf}
\caption{A comparison of the line rations of [N II]:\ha\ to that of [S II]:\ha for the SNR candidates. \label{fig_s2_n2}}
\end{figure}
